DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM

### 2022-05-08 paper.tex
only katy's comments left

\begin{figure}[t]
    \centering
    % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
    \hspace*{-0.2cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M4.png}
        \put(57,42.5){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
    \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
    \hspace*{-0.0cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/simulation_2/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
    \vspace*{-0.2cm}
    \caption[Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\)]{Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\) for \(\text{SNR}=20\,\text{dB}\). NPM for systems of (a) 4 nodes/channels and (b) 8 nodes/channels. The inset of (a) shows the base ring topology (black arrows) and all other possible connections (dashed black arrows).}
    \label{fig:perf_eval:NPM_over_time_exp2}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    % \hspace*{-0.2cm}\subfloat[][\(M\!=\!4\)]{\includegraphics[trim={0.3cm 0.35cm 0.3cm 0.3cm},clip,height=3.7cm]{python/plots/NPM_over_time_M4.png}\label{fig:perf_eval:NPM_over_time_M4}}
    \hspace*{-0.1cm}\subfloat[][]{\begin{overpic}[trim={0.3cm 0.35cm 0.8cm 0.3cm},clip,height=4cm]{python/simulation_2/plots/NPM_over_time_M4.png}
        \put(60,53){\includestandalone[trim={0.0cm 0.0cm 0.0cm 0},clip,scale=0.6]{tikz/topology_inset_simulation}}
    \end{overpic}\label{fig:perf_eval:NPM_over_time_M4}}
    \hspace*{0.3cm}\subfloat[][]{\includegraphics[trim={0.3cm 0.35cm 0.8cm 0.3cm},clip,height=4cm]{python/simulation_2/plots/NPM_over_time_M8.png}\label{fig:perf_eval:NPM_over_time_M8}}
    \vspace*{-0.2cm}
    \caption[Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\)]{Convergence behaviour with \(L\!=\!16\) for different values of \(\zeta\) for \(\text{SNR}=20\,\text{dB}\). NPM for systems of (a) 4 nodes/channels and (b) 8 nodes/channels. The inset of (a) shows the base ring topology (black arrows) and all other possible connections (dashed black arrows).}
    \label{fig:perf_eval:NPM_over_time_exp2}
\end{figure}
